A4V PCA

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_SexSpecificDEGs.V2.Rmd
overdue update

library(plotly)
library(edgeR)
library(goseq)
library(org.Dm.eg.db)
library(rrvgo)
library(VennDiagram)
library(pathview)
library(visNetwork)

@@

@@

Enrichment = function(sigs, bg){
  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=kegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=kegg.names[row.names(KEGG),1]

@@

```{r echo = F, include = F}
GO.Sim.PCA = function(use.data){
    pca <- prcomp(t(use.data), scale.=TRUE) 
    pc1=scale(pca$x[,1])
    pc2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(PC1=pc1,
                        PC2=pc2,
                        sdev=pca$sdev,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group = reducedTerms[row.names(use.data), "parentTerm"],
                        Score = reducedTerms[row.names(use.data), "score"],
                        Term = reducedTerms[row.names(use.data), "term"],
                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
                        Total = GO.data[row.names(use.data), "numInCat"],
                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))

@@

GO20 = function(GO.data, GO.ontology){
GO.data = GO.data[GO.data$ontology == GO.ontology,
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

@@

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched GO Terms",
           margin = m)

@@

KEGG20 = function(data){

  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]

data$term = data$Name
if(length(unique(data$term)) < length(data$term)){
  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
}  
data = data[20:1,]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

@@

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Name",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$Name,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched KEGG Terms",
           margin = m)

@@

@@

sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
A3 = A3[apply(meancpm[A3, c("A3FT", "A3MT", "S3FT", "S3MT")],MARGIN = 1, mean)>cutoff]
A3 = intersect(A3, row.names(FDR)[FDR$AvS3MT < 0.05])
A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FT < 0.05])

A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
A9 = A9[apply(meancpm[A9, c("A9FT", "A9MT", "S9FT", "S9MT")],MARGIN = 1, mean)>cutoff]
A9 = intersect(A9, row.names(FDR)[FDR$AvS9MT < 0.05])
A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FT < 0.05])

GR = setdiff(sigsGR.FxM, sigsWT.FxM)
GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
                           "GR.M1","GR.M2","GR.M3",
                           "WT.F1","WT.F2",
                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

T3 = A3
T9 = A9

Thorax Sex Specific DEGs
```{r echo = F}

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

sigsA3FvMH = row.names(FDR)[FDR[,'A3FvMH']<.05]
sigsS3FvMH = row.names(FDR)[FDR[,'S3FvMH']<.05]
sigsA9FvMH = row.names(FDR)[FDR[,'A9FvMH']<.05]
sigsS9FvMH = row.names(FDR)[FDR[,'S9FvMH']<.05]

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMH, sigsS3FvMH)
A3 = A3[apply(meancpm[A3, c("A3FH", "A3MH", "S3FH", "S3MH")],MARGIN = 1, mean)>cutoff]
A3 = intersect(A3, row.names(FDR)[FDR$AvS3MH < 0.05])
A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FH < 0.05])

A9 = setdiff(sigsA9FvMH, sigsS9FvMH)
A9 = A9[apply(meancpm[A9, c("A9FH", "A9MH", "S9FH", "S9MH")],MARGIN = 1, mean)>cutoff]
A9 = intersect(A9, row.names(FDR)[FDR$AvS9MH < 0.05])
A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FH < 0.05])

GR = setdiff(sigsGR.FxM, sigsWT.FxM)
GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
                           "GR.M1","GR.M2","GR.M3",
                           "WT.F1","WT.F2",
                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

H3=A3
H9=A9

Head Sex Specific DEGs
```{r echo = F}

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

sigsA3FvMA = row.names(FDR)[FDR[,'A3FvMA']<.05]
sigsS3FvMA = row.names(FDR)[FDR[,'S3FvMA']<.05]
sigsA9FvMA = row.names(FDR)[FDR[,'A9FvMA']<.05]
sigsS9FvMA = row.names(FDR)[FDR[,'S9FvMA']<.05]

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMA, sigsS3FvMA)
A3 = A3[apply(meancpm[A3, c("A3FA", "A3MA", "S3FA", "S3MA")],MARGIN = 1, mean)>cutoff]
A3 = intersect(A3, row.names(FDR)[FDR$AvS3MA < 0.05])
A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FA < 0.05])

A9 = setdiff(sigsA9FvMA, sigsS9FvMA)
A9 = A9[apply(meancpm[A9, c("A9FA", "A9MA", "S9FA", "S9MA")],MARGIN = 1, mean)>cutoff]
A9 = intersect(A9, row.names(FDR)[FDR$AvS9MA < 0.05])
A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FA < 0.05])

GR = setdiff(sigsGR.FxM, sigsWT.FxM)
GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
                           "GR.M1","GR.M2","GR.M3",
                           "WT.F1","WT.F2",
                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

A3=A3
A9=A9

Abdomen Sex Specific DEGs
```{r echo = F}

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

@@

sigs = T9##setdiff(T9,T3)
bg = row.names(FDR)

sigsKEY = GeneIDKey[sigs,]
sigs = na.omit(sigsKEY$Symbol)
bgKEY = GeneIDKey[bg,]
bg = na.omit(bgKEY$Symbol)

@@

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

@@

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
BP.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "CC"
CC.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "MF"
MF.GO.fig = GO20(GO.data, GO.ontology)

KEGG.fig = KEGG20(sig.cats[["KEGG"]])

@@

@@

treemapPlot(reducedTerms)

@@

```{r}

x <- counts
gr <- factor(substr(colnames(counts), 1, nchar(colnames(counts))-1))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- normLibSizes(y)
design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design)
fit <- glmQLFit(z, design)

contr = makeContrasts(A9MT - A9FT, levels=design)
qlf = glmQLFTest(fit, contrast=contr)
DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEdata = DEdata$table
A9MvFT = DEdata

```{r}

volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
                          FDR = -log2(FDR[T9, 'A9FvMT']),
                          FC = A9MvFT[T9, 'logFC'],
                          Color = 'grey',
                          size = 3*log(meancpm[T9,"A9MT"]),
                          M.cpm = meancpm[T9,"A9MT"],
                          F.cpm = meancpm[T9,"A9FT"],
                          SM.cpm = meancpm[T9,"S9MT"],
                          SF.cpm = meancpm[T9,"S9FT"],
                          GO.terms = "none")

```{r}

@@

specific.cat = specific.cat[5]
parent.category = 'response to biotic stimulus'
specific.kegg = "none"
specific.go =  '0031594'

@@

if(specific.cat ==  'parent.category'){
  rt = reducedTerms
}

if(specific.cat ==  'BP.parent.category'){
  rt = BP.reducedTerms
}

if(specific.cat ==  'MF.parent.category'){
  rt = MF.reducedTerms
}

@@

volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
                          FDR = -log2(FDR[T9, 'A9FvMT']),
                          FC = A9MvFT[T9, 'logFC'],
                          Color = 'grey',
                          size = 3*log(meancpm[T9,"A9MT"]),
                          M.cpm = meancpm[T9,"A9MT"],
                          F.cpm = meancpm[T9,"A9FT"],
                          SM.cpm = meancpm[T9,"S9MT"],
                          SF.cpm = meancpm[T9,"S9FT"],
                          GO.terms = "none")

@@

if(specific.cat == 'parent.category' | specific.cat == 'BP.parent.category' | specific.cat == 'MF.parent.category'){
  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  parent.genes = intersect(parent.genes, row.names(volcano.data))
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
  main.title = parent.category
}

@@

@@

```{r include = F}

>>>>

library(plotly)
library(edgeR)
library(goseq)
library(org.Dm.eg.db)
library(rrvgo)
library(VennDiagram)
library(pathview)
library(visNetwork)
library(pathview)
library(rstudioapi)
library(clusterProfiler)

@@

KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genesingo=as.list(org.Dm.egGO2ALLEGS)

@@

Enrichment = function(sigs, bg){
  sigsKEY = GeneIDKey[sigs,]
  sigs = na.omit(sigsKEY$Symbol)
  bgKEY = GeneIDKey[bg,]
  bg = na.omit(bgKEY$Symbol)

  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=kegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=kegg.names[row.names(KEGG),1]

@@

GO.Sim.PCA = function(use.data){
    pca <- prcomp(t(use.data), scale.=TRUE) 
    pc1=scale(pca$x[,1])
    pc2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(PC1=pc1,
                        PC2=pc2,
                        sdev=pca$sdev,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group = use.data[row.names(use.data), "parentTerm"],
                        Score = use.data[row.names(use.data), "score"],
                        Term = use.data[row.names(use.data), "term"],
                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
                        Total = GO.data[row.names(use.data), "numInCat"],
                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))

@@

GO20 = function(GO.data, GO.ontology, FC.data, FDR.data){
GO.data = GO.data[GO.data$ontology == GO.ontology,
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
data$Score = -log10(data$adjp)

temp = nchar(data$term)
data$label = data$term
data$label[temp > 40] = paste0(substr(data$term[temp>40], 1 ,35), "...")

data$term = factor(data$term, levels = c(unique(data$term)))
data$up = 0
data$down = 0
data$allup = 0
data$alldown = 0

sigs = names(FDR.data[FDR.data <= 0.05])

i = 1
while(i <= nrow(data)){
  go.id = row.names(data)[i]
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  go.genes = intersect(go.genes, names(FC.data))
  sig.go.genes = intersect(go.genes, sigs)
  go.FC = FC.data[go.genes]
  sig.go.FC = FC.data[sig.go.genes]

  data$allup[i] = length(go.FC[go.FC>0])
  data$alldown[i] = length(go.FC[go.FC<0])
  data$up[i] = length(sig.go.FC[sig.go.FC>0])
  data$down[i] = length(sig.go.FC[sig.go.FC<0])
  i = i +1
}

data$down = data$down * -1
data$alldown = data$alldown * -1

@@

fig <- plot_ly(data, 
               x = ~up, y = ~label, 
               type = 'bar',
               name = "Sig. Increased FC",
               marker = list(color = 'brown',
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nDE up: ", data$up,
                      "\nDE down: ", data$down,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    add_trace(x = ~down, 
              y ~term, 
              marker = list(color = 'steelblue', 
                            line = list(color = "black", width = 1.5)), 
              name = "Sig. Decreased FC")%>%

    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = paste0("Top 20 Most Enriched ",GO.ontology, " GO Terms"),
           margin = m, barmode = 'overlay')

@@

KEGG20 = function(KEGG.data, FC.data, FDR.data){

data = KEGG.data[, c("category", "Name","adjp", "numDEInCat", "numInCat")]

data$term = data$Name
if(length(unique(data$term)) < length(data$term)){
  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
}  
data = na.omit(data[data$Name != 'Metabolic pathways',])
data = data[20:1,]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))
data$up = 0
data$down = 0
data$allup = 0
data$alldown = 0

sigs = names(FDR.data[FDR.data <= 0.05])

i = 1
while(i <= nrow(data)){
  kegg.id = data$category[i]
  kegg.genes = names(kegg[grep(kegg.id, kegg)])
  kegg.genes = GeneIDKey[GeneIDKey$Symbol %in% kegg.genes, "FBgn"]
  kegg.genes = intersect(kegg.genes, names(FC.data))
  sig.kegg.genes = intersect(kegg.genes, sigs)
  kegg.FC = FC.data[kegg.genes]
  sig.kegg.FC = FC.data[sig.kegg.genes]
  data$allup[i] = length(kegg.FC[kegg.FC>0])
  data$alldown[i] = length(kegg.FC[kegg.FC<0])
  data$up[i] = length(sig.kegg.FC[sig.kegg.FC>0])
  data$down[i] = length(sig.kegg.FC[sig.kegg.FC<0])
  i = i +1
}

data$down = data$down * -1
data$alldown = data$alldown * -1

@@

fig <- plot_ly(data, 
               x = ~up, y = ~term, 
               type = 'bar',
               name = "Sig. Increased FC",
               marker = list(color = 'brown',
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nDE up: ", data$up,
                      "\nDE down: ", data$down,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    add_trace(x = ~down, 
              y ~term, 
              marker = list(color = 'steelblue', 
                            line = list(color = "black", width = 1.5)), 
              name = "Sig. Decreased FC")%>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = paste0("Top 20 Most Enriched ", GO.ontology, " GO Terms"),
           margin = m, barmode = 'overlay')

@@

KEGG.diagram = function(PathwayID, out.id, FC.data, FDR.data){
  ##KEGG Mapping Function
  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
    }
  Home = dirname(rstudioapi::getSourceEditorContext()$path)
  OutputDir = paste0(Home, "/KEGG_Image_Files/")
  setwd(OutputDir)
  sigs = names(FDR.data[FDR.data <= .05])
  deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])

  pv.out <- pathview(gene.data =  deg.data,
                   pathway.id = PathwayID,
                   species = "dme",
                   kegg.native = T,
                   limit=list(gene=c(-2,2)),
                   node.sum="max.abs",
                   low="royalblue",mid = "grey",high="firebrick",
                   out.suffix = out.id,
                   bins=list(genes=30))
  setwd(Home)
  knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png"))
}

##Using all DEGs from the A9MT vs S9MT comparison
### (no minimum mean cpm cutoff or background factor DEG exclusion)
```{r echo = F}

@@

##T9 = setdiff(row.names(FDR)[FDR[,'AvS9MT']<.05], row.names(FDR)[FDR[,'AvS9FT']<.05])
T9 = row.names(FDR)[FDR[,'AvS9MT']<.05]
T9 = T9[apply(meancpm[T9, c("A9FT", "A9MT", "S9FT", "S9MT")],MARGIN = 1, mean)>cutoff]

@@

sigs = T9
bg = row.names(FDR)

@@

CC.simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

CC.reducedTerms <- reduceSimMatrix(CC.simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

@@

FC.data = setNames(FC$AvS9MT, row.names(FC))
FDR.data = setNames(FDR$AvS9MT, row.names(FDR))

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
BP.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)

GO.ontology = "CC"
CC.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)

GO.ontology = "MF"
MF.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)

KEGG.data = sig.cats[["KEGG"]]
KEGG.fig = KEGG20(KEGG.data, FC.data, FDR.data)

@@

treemapPlot(CC.reducedTerms)

@@

```{r echo = F, include=T, message = F, fig.align='center'}

PathwayID = "04146"
out.id = 'AvS9T'
KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)

@@

@@

specific.cat = specific.cat[2]
parent.category = 'peroxisome'
specific.kegg = "none"
specific.go =  '0042579'

@@

specific.cat = 'none'

if(length(intersect(parent.category, CC.reducedTerms$parentTerm))){
  rt = CC.reducedTerms
  specific.cat = 'parent.category'
}

if(length(intersect(parent.category, BP.reducedTerms$parentTerm))){
  rt = BP.reducedTerms
  specific.cat = 'parent.category'
}

if(length(intersect(parent.category, MF.reducedTerms$parentTerm))){
  rt = MF.reducedTerms
  specific.cat = 'parent.category'
}

@@

volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
                          FDR = -log2(FDR[T9, 'AvS9MT']),
                          FC = FC[T9, 'AvS9MT'],
                          Color = 'grey',
                          size = 3*log(meancpm[T9,"A9MT"]),
                          M.cpm = meancpm[T9,"A9MT"],
                          F.cpm = meancpm[T9,"A9FT"],
                          SM.cpm = meancpm[T9,"S9MT"],
                          SF.cpm = meancpm[T9,"S9FT"],
                          GO.terms = "none")

@@

if(specific.cat == 'parent.category'){
  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  parent.genes = intersect(parent.genes, row.names(volcano.data))
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
  main.title = parent.category
}

@@

if(specific.cat == 'none'){
  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
  volcano.data$Color = 'honeydew'
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  go.genes = intersect(go.genes, row.names(volcano.data))
  volcano.data[go.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
}

@@

```{r echo = F, include = T}

category = 'neuromuscular junction'
plot.all = F
set.size = F

volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
                          FDR = -log2(FDR[T9, 'AvS9MT']),
                          MFC = FC[T9, 'AvS9MT'],
                          FFC = FC[T9, 'AvS9FT'],
                          ##size = 3*log(meancpm[T9,"A9MT"]),
                          size = -log2(FDR[T9, 'AvS9MT']),
                          M.cpm = meancpm[T9,"A9MT"],
                          F.cpm = meancpm[T9,"A9FT"],
                          SM.cpm = meancpm[T9,"S9MT"],
                          SF.cpm = meancpm[T9,"S9FT"],
                          GO.terms = "none",
                          Color = FC[T9, 'AvS9MT'] - FC[T9, 'AvS9FT'])
row.names(volcano.data) = T9

specific.cat = 'none'

if(length(intersect(category, sig.cats$GO$category))){
  specific.cat = 'specific.go'
  specific.go = sig.cats$GO$category[sig.cats$GO$category == category]
}

if(length(intersect(category, sig.cats$GO$term))){
  specific.cat = 'specific.go'
  specific.go = sig.cats$GO$category[sig.cats$GO$term == category]
}

if(length(grep(category, sig.cats$KEGG$Name))){
  specific.cat = 'specific.kegg'
  specific.kegg = sig.cats$KEGG$category[grep(category, sig.cats$KEGG$Name)]
}

if(length(grep(category, sig.cats$KEGG$category))){
  specific.cat = 'specific.kegg'
  specific.kegg = sig.cats$KEGG$category[grep(category, sig.cats$KEGG$category)]
}

if(length(intersect(category, CC.reducedTerms$parentTerm))){
  rt = CC.reducedTerms
  specific.cat = 'parent.category'
}

if(length(intersect(category, BP.reducedTerms$parentTerm))){
  rt = BP.reducedTerms
  specific.cat = 'parent.category'
}

if(length(intersect(category, MF.reducedTerms$parentTerm))){
  rt = MF.reducedTerms
  specific.cat = 'parent.category'
}

if(specific.cat == 'parent.category'){
  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  parent.genes = intersect(parent.genes, row.names(volcano.data))
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
  main.title = parent.category
}

if(plot.all == F){
  volcano.data = volcano.data[volcano.data$Color == "deeppink",]
}

fig = plot_ly(data = volcano.data,
              x = ~MFC,
              y = ~FFC,
              type = 'scatter',
              mode = 'markers',
              marker = list(colorscale = list(c(0,.45,1), c("firebrick","ivory", "royalblue")),
                            reversescale =T,
                             colorbar = list(title = "delta FC",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Color,
                             line = list(color = "black", width = 1.5),
                             size = volcano.data$size),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nMale FC: ", round(volcano.data$MFC,2),
                      "\nFemale FC: ", round(volcano.data$FFC,2),
                      "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
                      "\nA4V Female Thorax mean cpm: ", round(volcano.data$F.cpm, 1),
                      "\nSilent Male Thorax mean cpm: ", round(volcano.data$SM.cpm, 1),
                      "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
fig = fig %>% layout(title = main.title,
                     shapes = list(
                       type = "line",
                       line = list(color = "black", dash = 'dash', width = 2),
                       x0 = -10,
                       x1 = 10,
                       y0 = -10,
                       y1 = 10))

```{r echo = F, message = F}

FGO.data = Enrichment(row.names(FDR)[FDR$AvS9FT<.05], row.names(FDR))$GO
MGO.data = Enrichment(row.names(FDR)[FDR$AvS9MT<.05], row.names(FDR))$GO

ontology = "CC"
GO.data = MGO.data[MGO.data$ontology == ontology,
                  c("category", "term","adjp", "numDEInCat", "numInCat")]
GO.data$Female.adjp = FGO.data[row.names(GO.data), 'adjp']

data = GO.data[,c("term","numDEInCat", "numInCat", "category")]
data$MaleScore = -log10(GO.data$adjp)
data$FemaleScore = -log10(GO.data$Female.adjp)
data$term = factor(data$term, levels = c(unique(data$term)))
data$Fup = 0
data$Fdown = 0
data$Mup = 0
data$Mdown = 0
data$FmeanFC = 0
data$MmeanFC = 0

M.sigs = row.names(FDR[FDR$AvS9MT <= 0.05,])
F.sigs = row.names(FDR[FDR$AvS9FT <= 0.05,])
MFC = setNames(FC$AvS9MT, row.names(FC))
FFC = setNames(FC$AvS9FT, row.names(FC))

i = 1
while(i <= nrow(data)){
  go.id = row.names(data)[i]
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  Mgo.genes = intersect(go.genes, M.sigs)
  Fgo.genes = intersect(go.genes, F.sigs)
  data$Fup[i] = length(Fgo.genes[FFC[Fgo.genes]>0])
  data$Fdown[i] = length(Fgo.genes[FFC[Fgo.genes]<0])
  data$Mup[i] = length(Mgo.genes[MFC[Mgo.genes]>0])
  data$Mdown[i] = length(Mgo.genes[MFC[Mgo.genes]<0])
  if(length(Fgo.genes)>0){
    data$FmeanFC[i] = mean(FFC[Fgo.genes])
  }
  if(length(Mgo.genes)>0){
    data$MmeanFC[i] = mean(MFC[Mgo.genes])
  }
  i = i +1
}

data$MTotalxFC = (data$MmeanFC*(data$Mup + data$Mdown))
data$FTotalxFC = (data$FmeanFC*(data$Fup + data$Fdown))
